---
name: Charles-Étienne
surname: Lavoie

position: "PhD Candidate / President, nQuerio"
qualifications: "PhD (Cand.)"
address: "2281, Pie IX, Montréal (Québec) H1V 2E6"
phone: 438-393-2410
email: "celavoie96@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "333333"
urlcolor: blue
linkcolor: blue
output: 
  vitae::awesomecv:
    page_total: true
header-includes:
  - \usepackage[gen]{eurosym}
papersize: letterpaper
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#######################
#### SHORT VERSION ####
#######################

# Whether to print a shortened version of the CV
short <- FALSE

########################
#### PACKAGE SETUP #####
########################

# Required packages
library(vitae)
library(dplyr)
library(scholar)
library(patchwork)
library(rsvg)
library(kableExtra)
library(tidyverse)
library(easystats)
library(here)

language <- "EN"

# To format links throughout the CV
source("files/functions.R")

# Automatically bold your name in the publication section
author_bold <- "Lavoie, C. É."

########################
#### GOOGLE SCHOLAR ####
########################

# Specify your Google scholar profile
scholar.profile <- "6APjQ4AAAAAJ"

# Specify your Google scholar short author name
author.name <- "Charles-Étienne Lavoie"

headcolor <- "0a0a0a"

########################
##### INSTRUCTIONS #####
########################

# Change the order of sections below as desired.
# Edit the individual files ("childs") to edit the content as desired.
# Add `eval = !short` to code chunks to make them optional for the short version

# See all instructions and tips here: https://github.com/rempsyc/cv
```

My research integrates work psychology, self-determination theory, and advanced quantitative methods to examine motivation, work–family dynamics, and emotion regulation. I am fascinated by how carefully chosen designs and analyses can deepen our understanding of complex motivational processes such as by refining constructs and examining how they unfold across time and contexts using psychometrics and multilevel analyses. Committed to open science, I develop infrastructure like nQuerio and R tools to enhance reproducibility. In teaching, I empower students to design rigorous, meaningful studies (this CV is generated in R).

```{r Education parent, child=c('sections/education.Rmd')}
```

```{r Internships parent, child=c('sections/internships.Rmd')}
```

```{r Publications parent, child=c('sections/publications.Rmd')}
```

```{r Preprints parent, child=c('sections/preprints.Rmd'), eval = F}
```

```{r Awards parent, child=c('sections/awards.Rmd')}
```

```{r Grants parent, child=c('sections/grant.Rmd'), eval=F}
```

```{r Research Experience parent, child=c('sections/research_experience.Rmd')}
```

```{r Software parent, child=c('sections/software.Rmd'), eval=F}
```

```{r Professional Development parent, child=c('sections/professional_development.Rmd')}
```

```{r Teaching parent, child=c('sections/teaching.Rmd')}
```

```{r Invited talks parent, child=c('sections/invited_talks.Rmd'), eval = !short}
```

```{r Conference talks parent, child=c('sections/conference_talks.Rmd'), eval = !short}
```

```{r Conference posters parent, child=c('sections/conference_posters.Rmd'), eval = FALSE}
```

```{r Academic service parent, child=c('sections/service.Rmd'), eval = !short}
```

```{r Other Professional Experience parent, child=c('sections/other_professional_experience.Rmd')}
```

```{r Media coverage parent, child=c('sections/media_coverage.Rmd')}
```

```{r Varia parent, child=c('sections/varia.Rmd')}
```

```{r Leadership parent, child=c('sections/leadership.Rmd'), eval = F}
```

```{r References parent, child=c('sections/references.Rmd'), eval = F}
```

```{r Blogs parent, child=c('sections/blogs.Rmd'), eval = F}
```

```{r credit parent, child=c('sections/credit.Rmd'), eval = F}
```

*This CV is generated from a reproducible R Markdown source using the {vitae} package. Source: https://github.com/CharlesEtienneLavoie/cv*
